%!TEX TS-program = xelatex
    \documentclass[]{friggeri-cv}

    \begin{document}
\header{Julien }{Nyambal}{Julien.nyambal@gmail.com | 00 27 83 398 9020 | 3 Stiemens Street, Braamfontein, Johannesburg, South Africa | https://github.com/juliennyambal}
\section{education}
\begin{entrylist}
	
	\entry
	{- 2019}
	{University of the Witwatersrand, {\normalfont Master of Science in Computer Science (Machine Learning - Computer Vision)}}
	{Johannesburg, South Africa}
	{}
	  
	
	\entry
	{May 2017}
	{University of the Witwatersrand, {\normalfont Bachelor of Science (Honours) in Computer Science}}
	{Johannesburg, South Africa}
	{\emph{GPA: With Distinction}}
	  
	
	\entry
	{March 2015}
	{University of Zululand, {\normalfont Bachelor of Science in Computer Science \& Mathematics}}
	{Kwadlangezwa, South Africa}
	{}
	  
\end{entrylist}
\section{experience}
\begin{entrylist}
	      
	\entry
	{June 2017 – November 2017}
	{University of Witwatersrand, Teaching Assistant}
	{Johannesburg, South Africa}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=4pt]
		\item Marking assignments, tests, examinations, Tutoring students, Monitoring Laboratory work
		\end{itemize}}
	        
	      
	\entry
	{February 2013 – November 2014}
	{University of Zululand, Teaching Assistant}
	{Kwadlangezwa, South Africa}
	{\vspace{-3mm}\begin{itemize}[leftmargin=10pt,itemsep=4pt]
		\item Marking assignments, Tutoring students, Monitoring Laboratory work
		\end{itemize}}
	        
\end{entrylist}
\section{skills}
\begin{entrylist}
	\skill{}{Programming Languages: {\normalfont Python(fluent), Octave/Matlab, Java, Scala(basic), C++(basic), LateX, Shell (Bash)}}
	\skill{}{Frameworks: {\normalfont Caffe, Keras (Tensorflow), Nvidia DiGITS, Spyder, Git, Android Studio}}
	\skill{}{Operating Systems: {\normalfont Ubuntu Linux (Prefered), Windows, MacOS(basic)}}
\end{entrylist}
\section{projects}
\begin{entrylist}
	
	\entry
	{}
	{SmartDrive {\normalfont Android SDK, Java}}
	{}
	{SmartDrive has been designed to monitor the usage of the mobile phone while driving a car. SmartDrive blocks incoming SMSs and calls whilst the user is driving. SmartDrive has been built for Android devices. The system has been developed for android devices especially. I was the project leader, we delivered the system on time with minimal bugs.}
	  
	
	\entry
	{}
	{Online (Indigenous) Health Forum {\normalfont Java, CSS, HTML, Liferay, Microsoft Translate API}}
	{}
	{Online (Indigenous) Health Forum , name of my project has been developed to bridge the gap of languages by allow people using different to exchange ideas using the forum as if they were all writing the same language . This forum has been develop using the Liferay platform. In this project, my aim was to use Liferay framework to dynamically get the words and sentences from one side of the communication and translate it to the corresponding language on the other side. Java was mainly used with the Translator API from Microsoft.}
	  
	
	\entry
	{}
	{Automated Parking Space Detection {\normalfont Python, Caffe (GPU), nvidia DiGits}}
	{}
	{Developed an Automated Parking Space Detection using some Computer Vision and Machine Learning techniques. I have used opencv with Python to predict the occupancy of some parking spot given a parking spot. I trained my dataset using Nvidia Digits under Caffe.}
	  
	
	\entry
	{}
	{Automated Parking Space Detection {\normalfont Python, Keras, Octave/Matlab, Scikit-learn}}
	{}
	{Improving the Honours project for automatic detection and comparison between Support Vector Machines and Convolutional Neural Networks.}
	  
\end{entrylist}
\section{awards}
\begin{entrylist}
	\entry
	{2012}
	{Scholarship (Rector\textquotesingle{}s fund), University of Zululand}
	{University of Zululand}
	{Best achiever undergraduate student with annual average of above 80\% in all modules.}
	\entry
	{2013}
	{2nd Best Software Engineering group Project Leader (SmartDrive)}
	{University of Zululand}
	{Created and developed the second best working native android for my 2nd year group project. Receive an award of best project leader.}
	\entry
	{2014}
	{Best 3rd year Computer Science student in Faculty of Science}
	{University of Zululand}
	{}
	\entry
	{2016}
	{DST–CSIR Inter-bursary Support Programme Scholarship}
	{}
	{}
	\entry
	{2016}
	{ABSA - Most Commercially Viable Project - Computer Science}
	{University of the Witwatersrand}
	{Best poster presentation under the Most Commercially Viable Project category when presenting Honours projects to companies for external assessment.}
	\entry
	{2017}
	{DST–CSIR Inter-bursary Support Programme Scholarship}
	{}
	{}
	\entry
	{September 2017}
	{Won \textquotesingle{}Machine Learning: A probabilistic Perspective by Kevin Murphy\textquotesingle{} at the Deep Learning Indaba 2017}
	{Johannesburg}
	{Poster presentation awarded (Automated Parking Space Detection) for innovative use of deep learning techniques.}
\end{entrylist}
\ 
\end{document}