%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% Website: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
	\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-8pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
	\item\small{
		\textbf{#1}{: #2 \vspace{-2pt}}
	}
}

\newcommand{\resumeSubheading}[4]{
	\vspace{-1pt}\item
	\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{#1} & #2 \\
		\textit{\small#3} & \textit{\small #4} \\
	\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
	\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
	\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
	
	%----------HEADING-----------------
	\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
		\textbf{\href{https://juliennyambal.github.io/}{\Large Julien Nyambal}} & Email : \href{mailto:Julien.Nyambal@gmail.com}{Julien.Nyambal@gmail.com}\\
		\href{https://juliennyambal.github.io/}{https://juliennyambal.github.io} & Mobile : +27 83 398 9020 \\
	\end{tabular*}
	

	%-----------EXPERIENCE-----------------
	\section{Experience}
	\resumeSubHeadingListStart
	
	\resumeSubheading
	{Capitec Bank - Business bank}{Johannesburg, South Africa}
	{Senior Software Engineer, Machine Learning}{Sept 2022 - Present}
	\resumeItemListStart
	\resumeItem{Transaction Categorization}
	{Assist the team into building a system to dynamically categorize financial transactions performed by the clients either via EFT, Cards and another mean of moving money from one account to the other.}
	\resumeItem{Business Clients Credit Scoring}
	{Leverage retail and previous business users to build a data-driven lending solution, for credit product like overdraft, credit cards}
	\resumeItem{Credit Data Mart}
	{Building data structures and catalogs of the Business Banks into Dimensions and Facts. Units Tests and Deployments of those tables daily transactions.}
	\resumeItemListEnd
	
	\resumeSubheading
	{Entelect}{Johannesburg, South Africa}
	{Senior Software Engineer, Machine Learning - Consultant}{Dec 2019 - August 2022}
	\resumeItemListStart
	\resumeItem{Standard Bank Corporate Investment Banking - FX Tips}
	{Lead to team into building from scratch a recommendation engine to suggest Forex products to corporate investment clients. I was responsible for building the backend ETL process and assisting Data Scientists into using their models for the recommendation.}
	\resumeItem{Standard Bank Corporate Investment Banking - Internal Credit Market Data}
	{Built from scratch a system to replace a software license used by the bank to aggregate major financial institutions like Bloomberg and Reuters to provide a single state of to commodities. Responsible for the major ETL processes and backend delivery using API endpoints.}
	\resumeItem{Standard Bank South Africa - Internal Incident Reporting System RMP}
	{Enhance incident reporting in the banks systems using NLP and GraphDB asopposed to relational DB. It reduced human interaction and faster ticket assignment.}
	\resumeItem{Standard Bank South Africa - Personal Business Banking - Forex Customer Analysis}
	{POC to try to predict currency pair value using time series and RNN}	
	\resumeItemListEnd
	
	\resumeSubheading
	{Retro Rabbit}{Pretoria, South Africa}
	{Software Engineer, Machine Learning - Consultant}{April 2018 - Nov 2019}
	\resumeItemListStart
	\resumeItem{Avo By Nedbank}
	{Customizing offering to clients based on the spending habits, using the main Credit Bureaus data, through Building and evaluating models for client segmentation.}
	\resumeItem{Kalido}
	{Enabling clients to hire or provide services based on skills and proximity, using cutting-edge NLP techniques in the backend}
	\resumeItemListEnd
	
	\resumeSubheading
	{University of the Witwatersrand}{Johannesburg, South Africa}
	{Part-Time Lecturer}{Jan 2019 - Jan 2021}
	\resumeItemListStart
	\resumeItem{Classes}
	{Lectured Introduction to Computer Science: Python and C++, Computer Networking}
	\resumeItemListEnd
	
	\resumeSubHeadingListEnd
	
	%-----------CERTIFICATION-----------------
	\section{Certifications}
	\resumeSubHeadingListStart
	\item{
		{AWS Solutions Architect, AWS Cloud Practitioner, Azure AI Fundamentals, Azure Data Fundamentals, Azure Fundamental}
	}
	\resumeSubHeadingListEnd
	
	%-----------PROJECTS-----------------
%\section{Projects}
%\resumeSubHeadingListStart
%\resumeSubItem{Reech}
%{-}
%\resumeSubItem{Techova}
%{-}
%\resumeSubItem{Presence Detection}
%{-}
%\resumeSubHeadingListEnd
	
	%
	%--------PROGRAMMING SKILLS------------
	\section{Programming Skills}
	\resumeSubHeadingListStart
	\item{
		\textbf{Languages}{: R, Python, SQL, C++, Java}
		\hfill
		\textbf{Technologies}{: AWS, Azure, Docker, Kafka, Hadoop}
	}
	\resumeSubHeadingListEnd
	
	%-----------EDUCATION-----------------
	\section{Education}
	\resumeSubHeadingListStart
	\resumeSubheading
	{University of the Witwatersrand}{Johannesburg, South Africa}
	{PhD in Computer Science}{Jan. 2019 -- Dec. 2025}
	\resumeSubheading
	{University of the Witwatersrand}{Johannesburg, South Africa}
	{Master of Science in Computer Science}{Feb. 2017 -- Apr. 2018}
	\resumeSubheading
	{University of the Witwatersrand}{Johannesburg, South Africa}
	{Bachelor of Science with Honours in Computer Science;  GPA: 3.60}{Feb. 2016 -- Nov. 2016}
	\resumeSubheading
	{University of Zululand}{KwaDlangezwa, South Africa}
	{Bachelor of Science in Computer Science;  GPA: 3.2}{Feb. 2012 -- Nov. 2014}
	\resumeSubHeadingListEnd
	%-------------------------------------------
\end{document}